%% Package and Class "uiucthesis2014" for use with LaTeX2e.
\documentclass[edeposit,fullpage,hidelinks]{uiucthesis2018}

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\usepackage[version=4]{mhchem} % \ce{^{227}_{90}Th+}

\usepackage[acronym,toc]{glossaries}
\include{acros}

\usepackage{xspace}
\usepackage{graphics}
\usepackage{float} 
\newcommand{\Cycamore}{\textsc{Cycamore}\xspace}
\newcommand{\Cyclus}{\textsc{Cyclus}\xspace}
\newcommand{\minus}{\scalebox{0.65}[1.0]{$-$}}
\newcommand{\mycomment}[1]{}

\usepackage{placeins}
\usepackage{booktabs} % nice rules (thick lines) for tables
\usepackage{microtype} % improves typography for PDF

\usepackage[hyphens]{url}
\usepackage{hyperref}
%\usepackage{subfig}
\usepackage{hhline}
\usepackage{amsmath}
\usepackage{color}
\usepackage{multirow}
\usepackage{siunitx}
\usepackage{subcaption}
\sisetup{
    input-decimal-markers = .,input-ignore = {,},table-number-alignment = right,
    group-separator={,}, group-four-digits = true
}
\usepackage{fourier}
\usepackage{booktabs}
\newcommand\tab[1][1cm]{\hspace*{#1}}

\usepackage{threeparttable, tablefootnote}

%tikzpicture fit to page width
\usepackage{environ}
\makeatletter
\newsavebox{\measure@tikzpicture}
\NewEnviron{scaletikzpicturetowidth}[1]{%
  \def\tikz@width{#1}%
  \def\tikzscale{1}\begin{lrbox}{\measure@tikzpicture}%
  \BODY
  \end{lrbox}
  \pgfmathparse{#1/\wd\measure@tikzpicture}%
  \edef\tikzscale{\pgfmathresult}%
  \BODY
}

\usepackage{tabularx}
\newcolumntype{b}{>{\hsize=1.0\hsize}X}
\newcolumntype{q}{>{\hsize=0.5\hsize}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash\hsize=0.5\hsize}X}
\newcolumntype{z}{>{\hsize=0.75\hsize}X}
\newcolumntype{s}{>{\hsize=.5\hsize}X}
\newcolumntype{m}{>{\hsize=.75\hsize}X}

\usepackage{cleveref}
\usepackage{datatool}
\usepackage[numbers]{natbib}
\usepackage{notoccite}


\usepackage{tikz}
\usetikzlibrary{positioning, arrows, decorations, shapes}

\usetikzlibrary{shapes.geometric,arrows}
\tikzstyle{process} = [rectangle, rounded corners, minimum width=2.5cm, minimum height=1cm,text centered, draw=black, fill=blue!30]

\tikzstyle{object} = [ellipse, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=green!30]
\tikzstyle{objectr} = [ellipse, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=red!30]

\tikzstyle{empty} =  [rectangle, rounded corners, minimum width=2.5cm, minimum height=0.7cm,text centered, draw=black, fill=white!30]
\tikzstyle{arrow} = [thick,->,>=stealth]


\title{Analysis of and Comparison Between Reprocessing Methods in the Molten Salt Breeder Reactor}
\author{Luke Seifert}
\department{Nuclear, Plasma, Radiological Engineering}
%\schools{B.S., University of Illinois - Urbana Champaign, 2017}
\schools{}
\msthesis
\advisor{Madicken Munk}
%\advisor{Madicken Munk, Kathryn D. Huff}
\degreeyear{2023}
\committee{Madicken Munk \\ Tomasz Kozlowski}
%\committee{Assistant Professor Kathryn D. Huff, Adviser \\ Professor Segundo Lector }


\begin{document}
\maketitle

\frontmatter
%% Create an abstract that can also be used for the ProQuest abstract.
%% Note that ProQuest truncates their abstracts at 350 words.
\begin{abstract}

Liquid fueled molten salt reactor modeling can be challenging, as the fuel composition varies temporally and spatially.
Although these models are challenging, they are important for predicting reactor safety and performance during operation.
%Molten salt reactors have had many depletion models generated since being announced as a generation IV reactor.
%To maintain stability and limit chemical corrosion, often molten salt reactors utilize online reprocessing.
One of the reasons these models are challenging is the difficulty in capturing different physical phenomena which occur in different time scales.
%Modeling reprocessing in concert with depletion in liquid fueled molten salt reactors is complex due to different physical phenomena which occur in different time scales.
Over short time scales, one of these physical phenomena is the movement of delayed neutron precursors to less important regions of the reactor.
For longer time scales, one of these physical phenomena is online reprocessing, which includes adding fresh fuel and removing fission products from the reactor during operation and is the focus of this work.
Reprocessing is useful in liquid fueled molten salt reactors because it limits chemical corrosion and improves the neutron economy.
Reprocessing can be performed continuously during operation, referred to as online reprocessing, or in batches during outages, referred to as batchwise reprocessing.
%Among these models, one important aspect which is considered is the online reprocessing capabilities of a liquid fueled molten salt reactor.
%The online reprocessing includes adding fresh fuel and removing fission products from the reactor during operation, allowing for a more efficient neutron economy.
In order to simulate reprocessing computationally, there are two different mathematical approaches which are commonly implemented in the literature, called batchwise and continuous reprocessing.
%The continuous reprocessing method is more physically reflective of the operation in reality for any reactor which uses a continuous chemical reprocessing scheme.
The continuous reprocessing method is more physically reflective of reactors using a chemically continuous reprocessing scheme.
However, there are many works which have implemented batchwise reprocessing methods to simulate a physically continuous reprocessing process.
In this thesis, I show that continuous reprocessing and batchwise reprocessing methods are not interchangeable.
Using both methods on the same system shows that there are non-trivial differences in the results.
I also investigate the computational cost of different reprocessing methods by performing a depletion time step refinement study.
In this study, I found that continuous reprocessing allows for significantly larger time steps without large increases in error, which reduces computational cost.
However, continuous reprocessing does not necessarily keep the overall mass constant, thus potentially leading to a nonphysical solution.
I compare the differences between both methods while determining the effect of this nonphysical mass change caused by continuous reprocessing.
%Part of the comparison also looks at benefits to using batchwise reprocessing, which is able to maintain the net core mass so that the problem remains physical.
%Because continuous reprocessing does not necessarily keep the overall mass constant by balancing fresh fuel feeds with fission product removal, this is investigated.
%An increase to core mass without changing the core volume would result in an increased density, generating non-physical results.


\end{abstract}

\chapter*{Acknowledgments}

This material is based upon work supported under an Integrated University Program Graduate Fellowship.
Any opinions, findings, conclusions, or recommendations expressed in this publication are
those of the author(s) and do not necessarily reflect the views of the Department of Energy
Office of Nuclear Energy.

I would like to thank Andrei Rykhlevskii for his assistance with SaltProc and helpful advice.
I would also like to thank Oleksandr Yardas, Nathan Glaser, and Ceser Zambrano for proofreading this work.
Thanks should also go to Madicken Munk and Tomasz Kozlowski for reviewing this work.
I would like to thank Ondrej Chvala and Katy Huff for their assistance in the early stages of this work.
Many thanks as well to Shayan Shahbazi and Scott Richards for helping me further my understanding of much of the fundamental information in this work.
Finally, I thank the Advanced Reactors and Fuel Cycles group for their code reviews and comments on my results.


%% The thesis format requires the Table of Contents to come
%% before any other major sections, all of these sections after
%% the Table of Contents must be listed therein (i.e., use \chapter,
%% not \chapter*).  Common sections to have between the Table of
%% Contents and the main text are:
%%
%% List of Tables
%% List of Figures
%% List Symbols and/or Abbreviations
%% etc.

\tableofcontents
\listoftables
\listoffigures

%% Create a List of Abbreviations. The left column
%% is 1 inch wide and left-justified
%\chapter{List of Abbreviations}
%\printglossaries
%% Create a List of Symbols. The left column
%% is 0.7 inch wide and centered

\pagebreak
\mainmatter

\chapter{Introduction}
\input{introduction}

\chapter{Literature Review}
\input{litrev}

\chapter{Methodology}
\input{methods}

\chapter{Results}
\input{results}

\chapter{Conclusions}
\input{concs}

\chapter*{Appendix A: Batchwise Steady State Mass Derivation}
\input{appendixA}

\backmatter

\bibliographystyle{apalike}
\bibliography{bibliography}

\end{document}
\endinput
%%
%% End of file `thesis-ex.tex'.
